Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
fixing markdown tables in RREADME

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>%str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- NA","",.)
    )
  }) 
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) 
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything())
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything())
```

>>>>

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == " ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "NA","",.)
    )
  }) 
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```
